### 2014-10-17 simulation.Rmd
Adding `scons seed` that runs things w/ diff seeds.

## Fitted parameter values
```{r, echo=FALSE, results="asis"}
par_df = data.frame(value = model@results[["par"]], row.names = names(model@results[["par"]]))
pandoc.table(par_df, style="rmarkdown")
par_df$names = row.names(par_df)
par_df = par_df[grep("->", par_df$names),]
ggplot(par_df, aes(x = names, y = value)) +
    geom_bar(stat = "identity", fill="white", color="gray") +
    theme(axis.text.x = element_text(angle = 90))
```

```{r}
model
```

## Window sizes and amount of data used to fit
```{r, echo=FALSE, results="hide"}
# For some reason the code doesn't work if we don't print out some of the
# counts, but we can do it in a hidden block.
counts <- model@counts@counts
head(counts)
```

```{r, echo=FALSE}
cat("left window size:", model@counts@leftwin,
    "\ncomplete window size:", nchar(rownames(counts)[[1]]),
    "\ntotal counts:", sum(counts))
```

@@

>>>>

## Details
```{r, echo=FALSE, results="hide"}
# For some reason the code doesn't work if we don't print out some of the
# counts, but we can do it in a hidden block.
counts <- model@counts@counts
head(counts)
```

```{r, echo=FALSE}
cat("left window size:", model@counts@leftwin,
    "\ncomplete window size:", nchar(rownames(counts)[[1]]),
    "\ntotal counts:", sum(counts),
    "\ntime:", simseq.opt$tlen,
    "\nseed:", simseq.opt$seed
    )
```

@@

## Fitted parameter values
```{r, echo=FALSE, results="asis"}
time <- as.numeric(simseq.opt$tlen)
mr_compare <- data.frame(fit=model@mutrates / time)
mr_compare$names <- rownames(mr_compare)
simvalues= data.frame(names=mutnames(simseq.config$tip$mutpats),
                      simulated=simseq.config$tip$mutrates)
mr_compare <- merge(simvalues, mr_compare)
pandoc.table(mr_compare, style="rmarkdown")
```

The corresponding plot, where bars are the fit values, and points are the simulated values:
```{r, echo=FALSE, results="asis"}
ggplot(mr_compare, aes(x=names)) +
    geom_bar(aes(y=fit), stat = "identity", fill="white", color="gray") +
    geom_point(aes(y=simulated)) +
    theme(axis.text.x = element_text(angle = 90),
          axis.title.y = element_blank())
```
